Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-12 main.tex
decomp+merge
tiny changes

A graph $\gH=\tuple{\vH,\eH}$ is a \bfit{subgraph} of a graph
$\gG=\tuple{\vG,\eG}$ if $\vH\subseteq\vG$ and $\eH\subseteq\eG$. It
is \bfit{induced} if $v,w\in\vH$ and $vw\in\eG$ implies $vw\in\eH$.  A
graph is \bfit{$\gH$-free} if it does not contain $\gH$ as an induced
subgraph.  The graph $\Pfour$ is the (undirected) graph
$\tuple{\set{v_1, v_2, v_3, v_4},\set{v_1v_2, v_2v_3, v_3v_4}}$.  A
\bfit{cograph} is a $P_4$-free undirected graph. The interest in
cographs for our paper comes from the following well-known fact.

@@

Our second results is more surprising, as it is a very strong
decomposition result for first order logic.

@@

\begin{thm}\label{thm:decompositionA}
  For every derivation $\vlder{\FOKS}{\Deri}{A}{\ttt}$ there is a formula $A_1$, such that there is a derivation:
  \begin{equation*}
    \vlderivation{
      \vlde{\set{\wlD,\wrD,\cD}}{}{A}{
        \vlde{\FOMLS}{}{A_1}{
          \vlhy{\ttt}}}}}}}}
  \end{equation*}
\end{thm}

>>>>

A graph $\gH=\tuple{\vH,\eH}$ is a \bfit{subgraph} of a graph
$\gG=\tuple{\vG,\eG}$ if $\vH\subseteq\vG$ and $\eH\subseteq\eG$. It
is \bfit{induced} if $v,w\in\vH$ and $vw\in\eG$ implies $vw\in\eH$. An induced
subgraph of $\gG=\tuple{\vG,\eG}$ is uniquely determined by its set of vertices
$V$ and we denote it by $\gG[V]$.
A graph is \bfit{$\gH$-free} if it does not contain $\gH$ as an induced
subgraph.  The graph $\Pfour$ is the (undirected) graph
$\tuple{\set{v_1, v_2, v_3, v_4},\set{v_1v_2, v_2v_3, v_3v_4}}$.  A
\bfit{cograph} is a $P_4$-free undirected graph. The interest in
cographs for our paper comes from the following well-known fact.

@@

Our second result is more surprising, as it is a very strong
decomposition result for first order logic.

@@

\begin{thm}\label{thm:decompositionA}
  For every derivation $\vlder{\FOKS}{\Deri}{A}{\ttt}$ there is a formula $A_1$, such that there is a derivation:
  \begin{equation*}
    \vlderivation{
      \vlde{\set{\wlD,\wrD,\cD}}{}{A}{
        \vlde{\FOMLS}{}{A_1}{
          \vlhy{\ttt}}}}
  \end{equation*}
\end{thm}
